---
title: "morning-interactive"
format: html
execute:
  warning : false
editor: visual
---
```{r}
#| warning: false
#| message: true

# load libraries ----
library(tidyverse)
```

`head()`, `tail()`, and `dim()`

```{r}
#| warning: false
#| message: false
# do some data exploration with the starwars df
head(starwars, n = 10) 
tail(starwars, n = 10)
dim(starwars)
```
Create a ggplot (scatterplot) of character mass (y-axis) and height (x axis)
Update the color of the points so that color changes based on the value of mass
```{r}
#| warning: false
#| message: true
ggplot(starwars, aes(x = height, y = mass, color = mass)) +
  geom_point() +
  labs(x = "Height (cm)",
       y = "Mass (kg)",
       title = "Star Wars Example")
```

- create a histogram of character heights
-update the fill color (`fill`) to purple and the outside border line `color` of each histogram bin to orange
-update your code chunk options so that only your code and output graph appear in the rendered doc (no warnings or messages)
-update the axis labels
```{r}

#| fig-cap: "caption text"
#| fig-alt: "This is some alt text"
ggplot(starwars, aes(x = height)) +
  geom_histogram(fill = "purple", color = "orange") +
  labs(x = "Height (cm)",
       y = "Count")
  
```

`df$col_name`
```{r}
sw_height_mean <- round(x = mean(starwars$height, na.rm = TRUE),
                        digits = 3)


```

The mean height of all starwars characters is `r sw_height_mean`





